---
title: "Assignment 2 - Functions, iteration and debugging"
author: "FILL IN YOUR FULL NAME"
date: "`r format(Sys.time(), '%B %d, %Y | %H:%M:%S | %Z')`"
output:
  html_document:
    code_folding: show
    df_print: paged
    highlight: tango
    number_sections: no
    theme: cosmo
    toc: no
---
  
<style>
div.answer {background-color:#f3f0ff; border-radius: 5px; padding: 20px;}
</style>

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      error = FALSE,
                      message = FALSE,
                      warning = FALSE,
                      comment = NA)
```

<!-- Do not forget to input your Github username in the YAML configuration up there --> 

***

```{r, include = T}
# LOAD THE PACKAGES YOU ARE USING IN THIS CODE CHUNK library(nameofpackage)
```

<br>

***


### Task 1 - Fun with functions [5 points in total]

a) Program a function `ultimate_answer()` that always returns the number 42 regardless of which input is provided, and show that it works providing three function calls that test different input types! [2 points]

```{r}
# YOUR CODE HERE
```

b) Program a function `normalize()` that normalizes a numeric vector x to mean(x) = 0 and sd(x) = 1, and that provides flexibility in handling `NA`s! Then, using tidyverse functionality, apply it to all numeric (including integer) variables in the `starwars` dataset! [3 points]

```{r}
# YOUR CODE HERE
```

<br>

***

### Task 2 - Functional programming in practice [8 points in total]

The `unvotes` package (hosted both on [CRAN](https://cran.r-project.org/web/packages/unvotes/index.html) and [GitHub](https://github.com/dgrtwo/unvotes)) provides data on the voting history of countries in the [United Nations General Assembly](http://www.un.org/en/ga/), along with information such as date, description, and topics for each vote. The package contains three datasets: `un_votes`, providing the history of each country's votes, `un_roll_calls`, providing information on each roll call vote, and `un_roll_call_issues`, providing issue (topic) classifications of roll call votes. Check out the [database tutorial](https://github.com/dgrtwo/unvotes) if you want to make yourself familiar with the data structure. Then, work on the following tasks.

a) Calculate how often, on average, Germany agreed with the US on a vote in the UN general assembly since 1990. Votes where voting information for one of the countries is missing should be discarded. [3 points]

```{r}
# YOUR CODE HERE
```

<br>

b) Now, create a function, `votes_agreement_calculator()`, that takes country identifiers as well as a `year_min` argument as inputs and that returns the share of agreement in voting between any two specified countries as numeric value, for a time period specified with year >= `year_min`. The function should take the necessary data frames directly from the `unvotes` package. Then, test the function by computing the agreement rates for (a) the United States and Russia for votes cast in 2000 and later and (b) France and the UK for votes cast in 2000 and later! [3 points]

```{r}
# YOUR CODE HERE
```


<br>

c) Using `purrr` functionality, find out which three countries on average agreed with the US the most from the year 2000 on! [2 points]

```{r, eval = TRUE}
# YOUR CODE HERE
```

<br>

***

### Task 3 - Debugging code [3 points in total]

The following code snippet contains various bugs. Flag them and suggest a fix by adding a comment in the respective line. Example:

```{r, eval = FALSE}
library(Tidyverse) # BUG: typo in library(Tidyverse); should be library(tidyverse) instead
```

```{r, eval = FALSE}
# load packages
library(tidyverse)
library(countrycode)
library(Unvotes)
# get continents data
continents <- countrycode:codelist %>%
  select(continent, iso2c) %>%
  rename(country_code == iso2c)
un_votes <- left_join(x = un_votes, y = continents, by = country_code)
# get data on European UN votes
eu_un_votes <- left_join(un_votes, un_roll_calls, by = "rcid") %>%
  left_join(., un_roll_call_issues, by = "rcid") %>% 
  filter(continent == "Europe", 
         date >= "1991-01-01" & date <= "2021-12-31") %>% 
  drop_na(short_name)
# encode Europe's voting behavior numerically
eu_un_votes <- eu_un_votes %>% 
  mutate(yes_vt = if_else(vote == "yes", 1, 0)),
         no_vt = if_else(vote == "no", 1, 0),
         abstention = if_else(vote == "abstain", 1, 0))
# list top 10 most disagreed with UN resolutions
hated_un <- eu_un_votes %>%
  group_by(unres)
  summarise(sh_disagree_with = sum(no_vt,na.rm = T) / sum(c(yes_vt,no_vt, abstention), na.rm = T)) %>% 
  arrange(desc(sh_disagree_with)) %>% 
  head(10)
hated_un
``` 


